---
title: "Simple document"
output: github_document
---
```{r}
library(tidyverse)
```

Let's import the `FAS_litters.csv` csv.

```{r}
litters_df =
  read_csv("data/FAS_litters.csv")

litters_df =
  janitor::clean_names(litters_df)

litters_df
```

janitor是一个package，clean_names是其中的一个function

Import the same dataset using an absolute path

```{r}
litters_df_abs =
  read_csv("E:/DS1/DS-Lecture5/data_wrangling_i/data/FAS_litters.csv")

litters_df_abs =
  janitor::clean_names(litters_df_abs)

litters_df
```

```{r}
pups_df= 
  read_csv("data/FAS_pups.csv")

pups_df=
  janitor::clean_names(pups_df)

pups_df
```

## Look at data
```{r}
litters_df

head(litters_df)
#print 6 lines

tail(litters_df)
```

You can use `view` to see the whole dataset
```{r,eval=FALSE}
view(litters_df)
#????
```

Look at the summary of the data
```{r}
str(litters_df)

skimr::skim(litters_df)
```

##Options in `read_*`


```{r}
litters_df =
  read_csv(
    "data/FAS_litters.csv", 
    skip = 10,col_names = FALSE)
```

Look at NA values
```{r}
litters_df =
  read_csv(
    "data/FAS_litters.csv", 
    na = c("NA",19,"."))
```

Column types
change weight from dbl to char

```{r}
litters_df =
  read_csv(
    "data/FAS_litters.csv",
    col_types =
      cols(
        "GD0 weight" = col_character()
      )
    )
```

## Other file types

Import a xlsx file first.

```{r}
library(readxl)
mlb_df = 
read_excel("data/mlb11.xlsx")
```

Import a sas file.

```{r}
library(haven)
pulse_df =
  read_sas("data/public_pulse_data.sas7bdat")
```

Don't do `read.csv()` and `litters_df$Gr`

##Export data

We have code that "cleans" data and need to export the result
```{r}
litters_df_cleaned =
  read_csv("data/FAS_litters.csv")
litters_df_cleaned = 
  janitor::clean_names(litters_df_cleaned)
write_csv(litters_df_cleaned,"data/litters_cleaned.csv")
```